---
title:  A comparison of the behaviour of female and male wild boars after an encounter with the Wildschweinschreck
author: Sarah Helbling
---


## Abstract




## Introduction

Wild boar ( _Sus scrofa_ L.) populations in wide parts of Europe, including Switzerland, have sharply increased in the past decades ( _Goulding, 2003; Maissei et al., 2015_). The main reasons for this increase is the high availability of food in combination with the high reproductive rate of wild boars ( _Geisser, 2005_) . Wild boars often feed in maize and wheat fields ( _Henning, 1998_) causing a lot of damage to the farmers. There are several methods to keep wild boars away from the field, e.g., increasing hunting pressure, electrical fences and acoustic deterrence ( _Breton, 1994; Mazzoni della Stella et al., 1995; Suter & Eyholzer, 2010;Vassant, 1997_). 

In a study conducted between 2013 and 2017,  all the above mentioned methods were tested and compared, to determine how agricultural land and nature reserves can best be protected from damage by wild boars ( _Suter, Stoller, Sigrist, 2018_). The authors concluded, that acoustic deterrence is especially suitable directly after the sowing of crops and shortly before maize and wheat are ripe (german: Milchreife). In combination with a hightend hunting pressure, acoustic deterrence is even more effective, while electrical fences only keep wild boars away from field when built and maintained well.

The study mainly focused on a comparison of the deterrence methods, but ignored the social structure of wild boars. The social structure of wild boars might have an influence on the behaviour of female versus male wild boars, insofar as that adult males mostly live isolated, while females and young boars live together in herds ( _Bon et al., 1986; Rossell et al., 2004_). Considering this social structure, this project aims to compare female and male wild boars and their behaviour after an encounter with an acoustic deterrence.


## Material and Methods

The data for this project was collected in the context of the [Evalutation eiens akustischen Wildschwein-Vergrämungssystems](https://www.zhaw.ch/de/forschung/forschungsdatenbank/projektdetail/projektid/842/). Further information about this study can be found in the [final report](https://www.zhaw.ch/storage/hochschule/medien/bildmaterial/Schlussbericht_Wildschweinschreck.pdf) (language: German) of the study and the [R package](https://computationalmovementanalysis.github.io/ComputationalMovementAnalysisData/index.html) of the data. 

In the years 2013-2017 46 fields and 39 wild boars were studied. The acoustic deterrence system fundamentally consisted of two loudspeakers that played species-specific warning noises of different wild boar individuals. Non-species-specific warning noises such as human steps, human voices and sounds of gun shots were added to further deter wild boars ( _Suter, Stoller & Sigrist, 2018_). 

### Material

For the analysis the following data sets of the R package Computational Movement Analysis Data were used: 
-wildboar data: 
  -wildschwein_BE;
  -wildschwein_metadata.
-wildschwein schreck data: 
  -schreck_agenda;
  -schreck_locations.
  
### Methods

In order to determine the encounter of a wild boar with a acoustic deterrence location (detloc), all wild boar GPS points within a 500 m radius of the detloc were selected, as well as all points within a time window of one hour before and six hours after the initial encounter. 

The movement parameter "distance" or steplength was created using the Euclidean Distance between points, while speed is the distance divided by the timelag in between location fixes. As the sampling regime included a location fix every 15 min. between 17:00 and 05:00, and a location fix every three hours (08:00, 11:00, 14:00, 17:00) during the day.

```{r, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
``` 

```{r, include = FALSE}
library(ComputationalMovementAnalysisData)
library(dplyr)
library(lubridate)
library(sf)
library(ggplot2)
library(patchwork)
library(tmap)
```

```{r }
# Metadata
meta_d<-wildschwein_metadata
boars_sex<-meta_d%>%
  select(TierID,Sex)

# Boar data
boars<-wildschwein_BE
boars<-inner_join(boars, boars_sex, by="TierID")%>%
  st_as_sf(coords=c("E","N"), crs=2056, remove=FALSE)%>%
  distinct()

# Separating the boar data based on the sex
f_boars<-boars %>%
  filter(Sex=="f")%>%
  group_by(TierID)%>%
  arrange(DatetimeUTC, .by_group=TRUE)%>%
  tibble::rowid_to_column("rowid")
m_boars<-boars %>%
  filter(Sex=="m")%>%
  group_by(TierID)%>%
  arrange(DatetimeUTC, .by_group=TRUE)%>%
  tibble::rowid_to_column("rowid")

rm(boars, boars_sex)

# Deterrence data
det_loc<-schreck_locations
det_a<-schreck_agenda

# joining the deterrence locations and the deterrence agenda
deterrence<- inner_join(det_a, det_loc, by="id")
deterrence<-st_as_sf(deterrence, coords=c("lon", "lat"), crs=4326, remove=FALSE)
det_CH<-st_transform(deterrence, 2056)
det_CH<-select(det_CH, -kultur, -phase, -zaun, -jagddruck)
rm(deterrence, det_loc, det_a)

# colors
col_7<-c("#762a83", "#af8dc3", "#e7d4e8", "#d9f0d3", "#7fbf7b", "#1b7837","#00441b")
```
```{r, warning=FALSE}
# create different buffers around deterrence locations
det_buffer<-st_buffer(det_CH, 500)
det_buffer<-select(det_buffer, -ausrichtung_min, -ausrichtung_max)
# yes this method to create sectors is stupid, but neigher my R skills nor my trigonometry skills are enough to do this...
# and now I present to you the most human-error prone thing ever (trigonometry is hard... and creating functions too)
poly<- function(a, b, c, d){
  poly_1 = matrix(
    c(
      a[1], a[2],
      b[1], b[2],
      c[1], c[2],
      d[1], d[2],
      a[1], a[2]
    ), ncol=2, byrow=TRUE
  ) %>%
    list() %>%
    st_polygon
  poly_1<-st_sfc(poly_1, crs=2056)
}

r<-1000
geom<-det_CH$geometry
min<-det_CH$ausrichtung_min
max<-det_CH$ausrichtung_max
rad <- function (x){
  rad= x*pi/180
  return(rad)
}
# Nr1 - 80, 280
a<-as.numeric(geom[[1]])
b<-a+c(r*sin(rad(min[1])), r*cos(rad(min[1]))) # maybe I'll do this everywhere, but...
c<-a+c(0, r)
d<-a+c(-r*cos(rad(max[1]-270)), r*sin(rad(max[1]-270)))
# create polygon
buf_1<-st_difference(det_buffer[1,], poly(a, b, c, d))

# Nr2 same as det_1
buf_2<-buf_1

# Nr3 - 45, 225
a<-as.numeric(geom[[3]])
b<-a+c(r*sin(rad(min[3])), r*cos(rad(min[3])))
c<-a+c(r,-r)
d<-a+c(-r*sin(rad(max[3]-180)), -r*cos(rad(max[3]-180)))
# create polygon
buf_3<-st_intersection(det_buffer[3,], poly(a, b, c, d))
#sector_buffer<- rbind(sector_buffer, st_intersection(det_buffer[3,], poly(a, b, c, d))) - theoretically possible...

# Nr4 - 30, 180 
a<-as.numeric(geom[[4]])
b<-a+c(r*sin(rad(30)), r*cos(rad(30)))
c<-a+c(r,-r)
d<-a+c(0,-r)
# create polygon
buf_4<-st_intersection(det_buffer[4,], poly(a, b, c, d))

# Nr5 - same as Nr4 
buf_5<-buf_4

# Nr6  - 200, 280
a<-as.numeric(geom[[6]])
b<-a+c(-r*sin(rad(200-180)), -r*cos(200-180))
c<-a+c(-r, 0)
d<-a+c(-r*cos(rad(280-270)), r*sin(rad(280-270)))
# create polygon
buf_6<-st_intersection(det_buffer[6,], poly(a, b, c, d))

# Nr7 - same as Nr6
a<-as.numeric(geom[[7]])
b<-a+c(-r*sin(rad(200-180)), -r*cos(200-180))
c<-a+c(-r, 0)
d<-a+c(-r*cos(rad(280-270)), r*sin(rad(280-270)))
# create polygon
buf_7<-st_intersection(det_buffer[6,], poly(a, b, c, d))

# Nr8 - 160,330
a<-as.numeric(geom[[8]])
b<-a+c(r*cos(rad(160-90)), -r*sin(rad(160-90)))
c<-a+c(-r,-r)
d<-a+c(-r*cos(rad(330-270)), r*sin(rad(330-270)))
# create polygon
buf_8<-st_intersection(det_buffer[8,], poly(a, b, c, d))

# Nr9 - same as Nr8
buf_9<-buf_8

# Nr10 - 60, 315
a<-as.numeric(geom[[10]])
b<-a+c(r*sin(rad(60)), r*cos(rad(60)))
c<-a+c(0,r)
d<-a+c(-r*cos(rad(315-270)), r*sin(rad(315-270)))
# create polygon
buf_10<-st_difference(det_buffer[10,], poly(a, b, c, d))

# Nr11 - same as Nr10
buf_11<-buf_10

# Nr12 - 20, 180 
a<-as.numeric(geom[[12]])
b<-a+c(r*sin(rad(20)), r*cos(rad(20)))
c<-a+c(r,-r)
d<-a+c(0, -r)
# create polygon
buf_12<-st_intersection(det_buffer[12,], poly(a, b, c, d))

# Nr 13 - 40, 270
a<-as.numeric(geom[[13]])
b<-a+c(r*sin(rad(40)), r*cos(rad(40)))
c<-a+c(0, r)
d<-a+c(-r,0)
# create polygon
buf_13<-st_difference(det_buffer[13,], poly(a, b, c, d))

# Nr 14 - 90, 250
a<-as.numeric(geom[[14]])
b<-a+c(r,0)
c<-a+c(0,-r)
d<-a+c(-r*sin(rad(250-180)), -r*cos(rad(250-180)))
# create polygon
buf_14<-st_intersection(det_buffer[14,], poly(a, b, c, d))

# Nr 15 - 250, 340
a<-as.numeric(geom[[15]])
b<-a+c(-r*sin(rad(250-180)), -r*cos(rad(250-180)))
c<-a+c(-r, 0)
d<-a+c(-r*cos(rad(340-270)), r*sin(rad(340-270)))
# create polygon
buf_15<-st_intersection(det_buffer[15,], poly(a, b, c, d))

# Nr 16 - 140, 280
a<-as.numeric(geom[[16]])
b<-a+c(r*cos(rad(140-90)), -r*sin(rad(140-90)))
c<-a+c(-r,-r)
d<-a+c(-r*cos(rad(280-270)), r*sin(rad(280-270)))
# create polygon
buf_16<-st_intersection(det_buffer[16,], poly(a, b, c, d))

#nr 17
buf_17<-buf_16

# Nr 18 - 0, 180
a<-as.numeric(geom[[18]])
b<-a+c(0,r)
c<-a+c(r,0)
d<-a+c(0,-r)
# create polygon
buf_18<-st_intersection(det_buffer[18,], poly(a, b, c, d))

# Nr 19
buf_19<-buf_18

# Nr 20 - 140, 320
a<-as.numeric(geom[[20]])
b<-a+c(r*cos(rad(140-90)), -r*sin(rad(140-90)))
c<-a+c(-r,-r)
d<-a+c(-r*cos(rad(320-270)), r*sin(rad(320-270)))
# create polygon
buf_20<-st_intersection(det_buffer[20,], poly(a, b, c, d))

# nr 21
buf_21<-buf_20

# Nr 22 - 200, 270
a<-as.numeric(geom[[22]])
b<-a+c(-r*sin(rad(200-180)), -r*cos(rad(200-180)))
c<-a+c(-r,-r)
d<-a+c(-r,0)
# create polygon
buf_22<-st_intersection(det_buffer[22,], poly(a, b, c, d))

# Nr 23 - 130, 310
a<-as.numeric(geom[[23]])
b<-a+c(r*cos(rad(130-90)), -r*sin(rad(130-90)))
c<-a+c(-r,-r)
d<-a+c(-r*cos(rad(310-270)), r*sin(rad(310-270)))
# create polygon
buf_23<-st_intersection(det_buffer[23,], poly(a, b, c, d))

# Nr. 24 - 170, 350
a<-as.numeric(geom[[24]])
b<-a+c(r*cos(rad(170-90)), -r*sin(rad(170-90)))
c<-a+c(-r,-r)
d<-a+c(-r*cos(rad(350-270)), r*sin(rad(350-270)))
# create polygon
buf_24<-st_intersection(det_buffer[24,], poly(a, b, c, d))

# Nr 25 - 250, 90
a<-as.numeric(geom[[25]])
b<-a+c(r,0)
c<-a+c(r,-r)
d<-a+c(-r*sin(rad(250-180)), -r*cos(rad(250-180)))
# create polygon
buf_25<-st_difference(det_buffer[25,], poly(a, b, c, d))

# Nr 26 
buf_26<-buf_25

# Nr 27  40, 220
a<-as.numeric(geom[[27]])
b<-a+c(r*sin(rad(40)), r*cos(rad(40)))
c<-a+c(r, -r)
d<-a+c(-r*sin(rad(220-180)), -r*cos(rad(220-180)))
# create polygon
buf_27<-st_intersection(det_buffer[27,], poly(a, b, c, d))

# Nr 28 - 100, 280
a<-as.numeric(geom[[28]])
b<-a+c(r*cos(rad(100-90)), -r*sin(rad(100-90)))
c<-a+c(0, -r)
d<-a+c(-r*cos(rad(280-270)), r*sin(rad(280-270)))
# create polygon
buf_28<-st_intersection(det_buffer[28,], poly(a, b, c, d))

# Nr 29 - 80, 260
a<-as.numeric(geom[[29]])
b<-a+c(r*sin(rad(80)), r*cos(rad(80)))
c<-a+c(r,-r)
d<-a+c(-r*sin(rad(260-180)), -r*cos(rad(260-180)))
# create polygon
buf_29<-st_intersection(det_buffer[29,], poly(a, b, c, d))

# Nr 30
buf_30<-buf_29

#Nr 31 - 26, 260
a<-as.numeric(geom[[31]])
b<-a+c(r*sin(rad(26)), r*cos(rad(26)))
c<-a+c(0, r)
d<-a+c(-r*sin(rad(260-180)), -r*cos(rad(260-180)))
# create polygon
buf_31<-st_difference(det_buffer[31,], poly(a, b, c, d))

# Nr 32 
buf_32<-buf_31

#Nr 33 - 60, 240
a<-as.numeric(geom[[33]])
b<-a+c(r*sin(rad(60)), r*cos(rad(60)))
c<-a+c(r,-r)
d<-a+c(-r*sin(rad(240-180)), -r*cos(rad(240-180)))
# create polygon
buf_33<-st_intersection(det_buffer[33,], poly(a, b, c, d))

#Nr 34
buf_34<-buf_33

#Nr 35 - 44, 332
a<-as.numeric(geom[[35]])
b<-a+c(r*sin(rad(44)), r*cos(rad(44)))
c<-a+c(0,r)
d<-a+c(-r*cos(rad(332-270)), r*sin(rad(332-270)))
# create polygon
buf_35<-st_difference(det_buffer[35,], poly(a, b, c, d))

# Nr 36 - 46, 214 
a<-as.numeric(geom[[36]])
b<-a+c(r*sin(rad(46)), r*cos(rad(46)))
c<-a+c(r,-r)
d<-a+c(-r*sin(rad(214-180)), -r*cos(rad(214-180)))
# create polygon
buf_36<-st_intersection(det_buffer[36,], poly(a, b, c, d))

#Nr 37- 30, 210
a<-as.numeric(geom[[37]])
b<-a+c(r*sin(rad(30)), r*cos(rad(30)))
c<-a+c(0,-r)
d<-a+c(-r*sin(rad(210-180)),-r*cos(rad(210-180)))
# create polygon
buf_37<-st_intersection(det_buffer[37,], poly(a, b, c, d))

# Nr 38 - 82, 320
a<-as.numeric(geom[[38]])
b<-a+c(r*sin(rad(82)), r*cos(rad(82)))
c<-a+c(0,-r)
d<-a+c(-r*cos(rad(320-270)), r*sin(rad(320-270)))
# create polygon
buf_38<-st_difference(det_buffer[38,], poly(a, b, c, d))

# Nr 39 - 80, 180
a<-as.numeric(geom[[39]])
b<-a+c(r*sin(rad(80)), r*cos(rad(80)))
c<-a+c(r,-r)
d<-a+c(0,-r)
# create polygon
buf_39<-st_intersection(det_buffer[39,], poly(a, b, c, d))

# Nr 40 - 60, 300 
a<-as.numeric(geom[[40]])
b<-a+c(r*sin(rad(60)), r*cos(rad(60)))
c<-a+c(0,r)
d<-a+c(-r*cos(rad(300-270)), r*sin(rad(300-270)))
# create polygon
buf_40<-st_difference(det_buffer[40,], poly(a, b, c, d))

# Nr 41 - 45, 225
a<-as.numeric(geom[[41]])
b<-a+c(r*sin(rad(45)), r*cos(rad(45)))
c<-a+c(r, -r)
d<-a+c(-r*sin(rad(225-180)), -r*cos(rad(225-180)))
# create polygon
buf_41<-st_intersection(det_buffer[41,], poly(a, b, c, d))

# Nr 42 - 100, 225
a<-as.numeric(geom[[42]])
b<-a+c(r*cos(rad(100-90)), -r*sin(rad(100-90)))
c<-a+c(0,-r)
d<-a+c(-r*sin(rad(225-180)), -r*cos(rad(225-180)))
# create polygon
poly_42<-poly(a, b, c, d)
buf_42<-st_intersection(det_buffer[ 42,], poly(a, b, c, d))

# Nr 43 - 180, 270
a<-as.numeric(geom[[43]])
b<-a+c(0,-r)
c<-a+c(-r,-r)
d<-a+c(-r,0)
# create polygon
buf_43<-st_intersection(det_buffer[ 43,], poly(a, b, c, d))

# Nr 44 - 170, 260
a<-as.numeric(geom[[44]])
b<-a+c(r*cos(rad(170-90)), -r*sin(rad(170-90)))
c<-a+c(-r,-r)
d<-a+c(-r*sin(rad(260-180)), -r*cos(rad(260-180)))
# create polygon
buf_44<-st_intersection(det_buffer[44,], poly(a, b, c, d))

# Nr 45 - 60, 240
a<-as.numeric(geom[[45]])
b<-a+c(r*sin(rad(60)), r*cos(rad(60)))
c<-a+c(r,-r)
d<-a+c(-r*sin(rad(240-180)), -r*cos(rad(240-180)))
# create polygon
buf_45<-st_intersection(det_buffer[45,], poly(a, b, c, d))

# Nr 46 - 260, 330
a<-as.numeric(geom[[46]])
b<-a+c(-r*sin(rad(260-180)), -r*cos(rad(260-180)))
c<-a+c(-r, 0)
d<-a+c(-r*cos(rad(330-270)), r*sin(rad(330-270)))
# create polygon
buf_46<-st_intersection(det_buffer[46,], poly(a, b, c, d))

# Nr 47 - 190, 350 
a<-as.numeric(geom[[47]])
b<-a+c(-r*sin(rad(190-180)), -r*cos(rad(190-180)))
c<-a+c(-r,0)
d<-a+c(-r*cos(rad(350-270)), r*sin(rad(350-270)))
# create polygon
buf_47<-st_intersection(det_buffer[47,], poly(a, b, c, d))

# Nr 48 - 180, 340
a<-as.numeric(geom[[48]])
b<-a+c(0,-r)
c<-a+c(-r,0)
d<-a+c(-r*cos(rad(340-270)), r*sin(rad( 340-270)))
# create polygon
buf_48<-st_intersection(det_buffer[48,], poly(a, b, c, d))

# Nr 49 - 20, 230
a<-as.numeric(geom[[49]])
b<-a+c(r*sin(rad(20)), r*cos(rad(20)))
c<-a+c(-r,r)
d<-a+c(-r*sin(rad(230-180)), -r*cos(rad(230-180)))
# create polygon
buf_49<-st_difference(det_buffer[49,], poly(a, b, c, d))

# Nr 50 - 50, 230
a<-as.numeric(geom[[50]])
b<-a+c(r*sin(rad(50)), r*cos(rad(50)))
c<-a+c(r,-r)
d<-a+c(-r*sin(rad(230-180)), -r*cos(rad(230-180)))
# create polygon
buf_50<-st_intersection(det_buffer[50,], poly(a, b, c, d))

# Nr 51 - 110, 190
a<-as.numeric(geom[[51]])
b<-a+c(r*cos(rad(110-90)), -r*sin(rad(110-90)))
c<-a+c(0,-r)
d<-a+c(-r*sin(rad(190-180)), -r*cos(rad(190-180)))
# create polygon
buf_51<-st_intersection(det_buffer[51,], poly(a, b, c, d))

# Nr 52 - 30, 220
a<-as.numeric(geom[[52]])
b<-a+c(r*sin(rad(30)), r*cos(rad(30)))
c<-a+c(-r, r)
d<-a+c(-r*sin(rad(220-180)), -r*cos(rad(220-180)))
# create polygon
buf_52<-st_difference(det_buffer[52,], poly(a, b, c, d))

# Nr 53 - 60, 240
a<-as.numeric(geom[[53]])
b<-a+c(r*sin(rad(60)), r*cos(rad(60)))
c<-a+c(r, -r)
d<-a+c(-r*sin(rad(240-180)), -r*cos(rad(240-180)))
# create polygon
buf_53<-st_intersection(det_buffer[53,], poly(a, b, c, d))

# Nr 54 - 0, 180
a<-as.numeric(geom[[54]])
b<-a+c(0, r)
c<-a+c(r,0)
d<-a+c(0,-r)
# create polygon
buf_54<-st_intersection(det_buffer[54,], poly(a, b, c, d))

# Nr 55 - 110, 280
a<-as.numeric(geom[[55]])
b<-a+c(r*cos(rad(110-90)), -r*sin(rad(110-90)))
c<-a+c(-r, -r)
d<-a+c(-r*cos(rad(280-270)), r*sin(rad(280-270)))
# create polygon
buf_55<-st_intersection(det_buffer[55,], poly(a, b, c, d))

# Nr 56 - 160, 260
a<-as.numeric(geom[[56]])
b<-a+c(r*cos(rad(160-90)), -r*sin(rad(160-90)))
c<-a+c(0, -r)
d<-a+c(-r*sin(rad(260-180)), -r*cos(rad(260-180)))
# create polygon
buf_56<-st_intersection(det_buffer[56,], poly(a, b, c, d))

# Nr 57 - 0, 250
a<-as.numeric(geom[[57]])
b<-a+c(0,r)
c<-a+c(-r,r)
d<-a+c(-r*sin(rad(250-180)), -r*cos(rad(250-180)))
# create polygon
buf_57<-st_difference(det_buffer[57,], poly(a, b, c, d))

# Nr 58 - 0, 150
a<-as.numeric(geom[[58]])
b<-a+c(0, r)
c<-a+c(r,0)
d<-a+c(r*cos(rad(150-90)), -r*sin(rad(150-90)))
# create polygon
buf_58<-st_intersection(det_buffer[58,], poly(a, b, c, d))

# Nr 59 - 260, 310
a<-as.numeric(geom[[59]])
b<-a+c(-r*sin(rad(260-180)), -r*cos(rad(260-180)))
c<-a+c(-r,0)
d<-a+c(-r*cos(rad(310-270)), r*sin(rad(310-270)))
# create polygon
buf_59<-st_intersection(det_buffer[59,], poly(a, b, c, d))

# Nr 60 - 170, 270
a<-as.numeric(geom[[60]])
b<-a+c(r*cos(rad(170-90)), -r*sin(rad(170-90)))
c<-a+c(0,-r)
d<-a+c(-r, 0)
# create polygon
buf_60<-st_intersection(det_buffer[60,], poly(a, b, c, d))

# Nr 61- 45, 315
a<-as.numeric(geom[[61]])
b<-a+c(r*sin(rad(45)), r*cos(rad(45)))
c<-a+c(0,r)
d<-a+c(-r*cos(rad(315-270)), r*sin(rad(315-270)))
# create polygon
buf_61<-st_difference(det_buffer[61,], poly(a, b, c, d))

# Nr62 - 90, 315
a<-as.numeric(geom[[62]])
b<-a+c(r,0)
c<-a+c(r,r)
d<-a+c(-r*cos(rad(315-270)))
# create polygon
buf_62<-st_difference(det_buffer[62,], poly(a, b, c, d))

# Nr 63 - 60, 240
a<-as.numeric(geom[[63]])
b<-a+c(r*sin(rad(60)), r*cos(rad(60)))
c<-a+c(r,-r)
d<-a+c(-r*sin(rad(240-180)), -r*cos(rad(240-180)))
# create polygon
buf_63<-st_intersection(det_buffer[63,], poly(a, b, c, d))

# Nr 64 same as 63
buf_64<-buf_63

# Nr 65 - 0, 110
a<-as.numeric(geom[[65]])
b<-a+c(0, r)
c<-a+c(r,0)
d<-a+c(r*cos(rad(110-90)), -r*sin(rad(110-90)))
# create polygon
buf_65<-st_intersection(det_buffer[65,], poly(a, b, c, d))

# Nr 66 - 90, 200
a<-as.numeric(geom[[66]])
b<-a+c(r,0)
c<-a+c(r,-r)
d<-a+c(-r*sin(rad(200-180)), -r*cos(rad(200-180)))
# create polygon
buf_66<-st_intersection(det_buffer[66,], poly(a, b, c, d))

# Nr 67 - 150, 300
a<-as.numeric(geom[[67]])
b<-a+c(r*cos(rad(150-90)), -r*sin(rad(150-90)))
c<-a+c(-r,-r)
d<-a+c(-r*cos(rad(300-270)), r*cos(rad(300-270)))
# create polygon
buf_67<-st_intersection(det_buffer[67,], poly(a, b, c, d))

# Nr 68 - 250, 340
a<-as.numeric(geom[[68]])
b<-a+c(-r*sin(rad(250-180)), -r*cos(rad(250-180)))
c<-a+c(-r,0)
d<-a+c(-r*cos(rad(340-270)), r*sin(rad(340-270)))
# create polygon
buf_68<-st_intersection(det_buffer[68,], poly(a, b, c, d))

# Nr 69 - 50, 250
a<-as.numeric(geom[[69]])
b<-a+c(r*sin(rad(50)), r*cos(rad(50)))
c<-a+c(-r, r)
d<-a+c(-r*sin(rad(250-180)), -r*cos(rad(250-180)))
# create polygon
buf_69<-st_intersection(det_buffer[69,], poly(a, b, c, d))

buf_sector<- rbind(buf_1, buf_2, buf_3, buf_4, buf_5, buf_6, buf_7, buf_8, buf_9, buf_10,
                   buf_11, buf_12, buf_13, buf_14, buf_15, buf_16, buf_17, buf_18, buf_19, buf_20,
                   buf_21, buf_22, buf_23, buf_24, buf_25, buf_26, buf_27, buf_28, buf_29, buf_30,
                   buf_31, buf_32, buf_33, buf_34, buf_35, buf_36, buf_37, buf_38, buf_39, buf_40,
                   buf_41, buf_42, buf_43, buf_44, buf_45, buf_46, buf_47, buf_48, buf_49, buf_50,
                   buf_51, buf_52, buf_53, buf_54, buf_55, buf_56, buf_57, buf_58, buf_59, buf_60,
                   buf_61, buf_62, buf_63, buf_64, buf_65, buf_66, buf_67, buf_68, buf_69)

rm(buf_1, buf_2, buf_3, buf_4, buf_5, buf_6, buf_7, buf_8, buf_9, buf_10,
   buf_11, buf_12, buf_13, buf_14, buf_15, buf_16, buf_17, buf_18, buf_19, buf_20,
   buf_21, buf_22, buf_23, buf_24, buf_25, buf_26, buf_27, buf_28, buf_29, buf_30,
   buf_31, buf_32, buf_33, buf_34, buf_35, buf_36, buf_37, buf_38, buf_39, buf_40,
   buf_41, buf_42, buf_43, buf_44, buf_45, buf_46, buf_47, buf_48, buf_49, buf_50,
   buf_51, buf_52, buf_53, buf_54, buf_55, buf_56, buf_57, buf_58, buf_59, buf_60,
   buf_61, buf_62, buf_63, buf_64, buf_65, buf_66, buf_67, buf_68, buf_69, r, geom, min, max, a,b,c,d)
```
```{r }
# join
f_join_sector<-st_join(f_boars, buf_sector, left=FALSE)
m_join_sector<-st_join(m_boars, buf_sector, left=FALSE)

# check if deterrence was active during the encounter
f_join_sector<-f_join_sector %>%
  mutate(active=DatetimeUTC %within%interval((ymd(datum_on)+hours(-12)),
                                             (ymd(datum_off)+hours(12)))) %>%
  filter(active==TRUE)%>%
  distinct()

m_join_sector<-m_join_sector %>%
  mutate(active=DatetimeUTC %within%interval((ymd(datum_on)+hours(-12)),
                                             (ymd(datum_off)+hours(12)))) %>%
  filter(active==TRUE)%>%
  distinct()

# removing points with consecutive rowids' to avoid counting the same encounter several times
f_unique<-f_join_sector %>%
  mutate(id_diff=abs(rowid-lag(rowid, default = 46))) %>%
 filter(id_diff>46)
m_unique<-m_join_sector %>%
  mutate(id_diff=abs(rowid-lag(rowid, default = 46))) %>%
  filter(id_diff>46)

## ID_diff >46 is based on the idea, that, in a later step, all those IDs get selected that are within a 12h time-window of this one ID (that encounter) if IDs are still in there that are too close together they are going to be selected as separate encounters --> it might not perfectly reflect the 6h before and 6h after an encounter, but it is a compromise that helps to avoid having seemingly different encounters despite the wild boar not even having left the buffer-zone in the first place
rm( f_join_sector, m_join_sector)
```
```{r }
#Function to filter for those points that are within a given time window and belong to a certain animal
inInterval<-function(boardata, timewindow, animalID){
  filter(boardata, DatetimeRound %within% timewindow,
         TierID==animalID)
}
```
```{r }
# preparing the encounter data
f_timewindows<-f_unique %>%
  mutate(DatetimeRound=round_date(DatetimeUTC, "15 minutes"),
         Timewindow=interval(DatetimeRound+hours(-6), DatetimeRound+hours(6))) %>%
  distinct()

m_timewindows<-m_unique %>%
  mutate(DatetimeRound=round_date(DatetimeUTC, "15 minutes"),
         Timewindow=interval(DatetimeRound+hours(-6), DatetimeRound+hours(6))) %>%
  distinct()

# prepare the boars data
f_boars<-mutate(f_boars, DatetimeRound=round_date(DatetimeUTC, "15 minutes"))
m_boars<-mutate(m_boars, DatetimeRound=round_date(DatetimeUTC, "15 minutes"))
```
```{r }

# filter out all the relevant rowids that reflect point 6h before and 6h after an encounter
#females
rowid<-numeric()
meetings<-numeric()
meet_id<-numeric()
nr_rows<-c(1:nrow(f_timewindows))
for (i in nr_rows){
  match=inInterval(f_boars, f_timewindows$Timewindow[i], f_timewindows$TierID[i])
  match=distinct(match)
  rowid=c(rowid, match$rowid)
  len=nrow(match)
  meetings=c(meetings,len)
  meet_id=c(meet_id,rep(i, times=meetings[i]))
}
#filter for all relevant data points from the females dataset
matches<-as.data.frame(rowid)
matches<-cbind(matches, meet_id)
f_relevant<-matches %>%
  inner_join(f_boars, by="rowid") %>%
  distinct() %>%
  st_as_sf(crs=2056) %>%
  select(rowid, meet_id, DatetimeRound, geometry, E, N) %>% 
  group_by(meet_id)
```
```{r }
# males
rowid<-numeric()
meetings<-numeric()
meet_id<-numeric()
nr_rows<-c(1:nrow(m_timewindows))
for (i in nr_rows){
  match=inInterval(m_boars, m_timewindows$Timewindow[i], m_timewindows$TierID[i])
  match=distinct(match)
  rowid=c(rowid, match$rowid)
  len=nrow(match)
  meetings=c(meetings,len)
  meet_id=c(meet_id,rep(i, times=meetings[i]))
}
# filter all relevant data points from the females dataset
matches<-as.data.frame(rowid)
matches<-cbind(matches, meet_id)
m_relevant<-matches %>%
  inner_join(m_boars, by="rowid") %>%
  distinct() %>%
  st_as_sf(crs=2056) %>%
  select(rowid, meet_id, DatetimeRound, geometry, E, N) %>%
  group_by(meet_id)


rm(meet_id,meetings, nr_rows,i,len, matches, match, rowid, f_timewindows,m_timewindows)
```
```{r }
# join the encounters once again with features of the deterrence

f_rel<-f_relevant %>%
  st_drop_geometry()%>%
  select(rowid, meet_id)

m_rel<-m_relevant %>%
  st_drop_geometry()%>%
  select(rowid, meet_id)


# prepare deterrence features
f_det<-f_unique %>%
  st_drop_geometry() %>%
  select(rowid, TierName, id, modus, lautstaerke, intervall)

m_det<-m_unique %>%
  st_drop_geometry() %>%
  select(rowid, TierName, id, modus, lautstaerke, intervall)


f_deterrence<-inner_join(f_rel, f_det, by="rowid")
m_deterrence<-inner_join(m_rel, m_det, by="rowid")

```
```{r }
# finally prepare for the join of the relevant points with the available deterrence data
f_rel<-f_relevant %>%
  st_drop_geometry() %>%
  select(rowid, meet_id, DatetimeRound, E, N)
m_rel<-m_relevant %>%
  st_drop_geometry() %>%
  select(rowid, meet_id, DatetimeRound, E, N)


f_joined<-left_join(f_rel, f_deterrence, by="meet_id")
m_joined<-left_join(m_rel, m_deterrence, by="meet_id")

f_encounters<- st_as_sf(f_joined, coords=c("E","N"), crs=2056, remove=FALSE)
m_encounters<- st_as_sf(m_joined, coords=c("E","N"), crs=2056, remove=FALSE)

rm(f_rel, m_rel, f_det, m_det,f_deterrence, m_deterrence, f_joined, m_joined, f_relevant,m_relevant)
```
```{r, include=FALSE}
length(unique(f_encounters$rowid.x))==nrow(f_encounters)
nrow(f_encounters)/length(unique(f_encounters$meet_id)) 
# 12h should technically (with the 15min. sampling interval) result in 48 points, but since sampling is only every few hours during the day, it's only logical as I selected by "within time interval" and not +/- a certain number of ids'
length(unique(m_encounters$rowid.x))==nrow(m_encounters)
nrow(m_encounters)/length(unique(m_encounters$meet_id))

```

```{r }
# getting an overview
#plotting all movements of female wild boars within a 12h window of an encounter with a deterrence
f_sector<-filter(buf_sector, id %in% unique(f_encounters$id))
m_sector<-filter(buf_sector, id %in% unique(m_encounters$id))

# f_encounters_buffer<-ggplot()+
#   geom_sf(data=f_sector, fill="grey", alpha=.4, color="grey")+
#   geom_sf(data=f_encounters, aes(colour=meet_id), size=0.4)+
#   geom_path(data=f_encounters, aes(E, N), color="grey", alpha=0.5)+
#   #facet_wrap(~meet_id)+
#   theme(legend.position = "none")+
#   coord_sf(datum=2056)+
#   xlim(2568000, 2575000)+
#   ylim(1202000, 1208000)


```

```{r }
# m_encounters_buffer<-ggplot()+
#   geom_sf(data=m_sector, fill="grey", alpha=0.4, color="grey")+
#   geom_path(data=m_encounters, aes(E, N), color="grey", alpha=0.5)+
#   geom_sf(data=m_encounters, aes(color=meet_id),size=0.5)+
#   #facet_wrap(~meet_id)+
#   theme(legend.position = "none")+
#   coord_sf(datum=2056)+
#   xlim(2568000, 2575000)+
#   ylim(1202000, 1208000)
```

```{r }
# deriving movement parameters
f_encounters<- f_encounters %>%
  group_by(meet_id) %>%
  mutate(timelag = as.numeric(difftime(lead(DatetimeRound),DatetimeRound, units = "secs")),
         steplength=sqrt((E-lead(E,1))^2+(N-lead(N,1))^2),
         speed=steplength/timelag)

m_encounters<- m_encounters %>%
  group_by(meet_id) %>%
  mutate(timelag = as.numeric(difftime(lead(DatetimeRound),DatetimeRound, units = "secs")),
         steplength=sqrt((E-lead(E,1))^2+(N-lead(N,1))^2),
         speed=steplength/timelag)
```

Bounding box of all points of f/m_encounters
   xmin    ymin    xmax    ymax 
2'568'440 1'202'900 2'574'921 1'207'596 

```{r }
boden<-read_sf("C:/Users/sarah/OneDrive - ZHAW/ACLS/Track_Module/project/Project-template-master/Project-template-master/tlm_bodenbedeckung/TLM3D_bodenbedeckung.shx")
boden<-boden %>%
  select(objektart) %>%
  st_transform(2056)

umgebung<-st_as_sfc(st_bbox(rbind(f_encounters, m_encounters)))  # it is not perfect, but for the sake of this project probably close enough
landwirtschaft<-st_difference(umgebung, st_combine(st_union(boden)))
landwirtschaft <- landwirtschaft %>%
  st_as_sf()%>%
  mutate(objektart=1000) %>%
  select(objektart)
st_geometry(landwirtschaft)<-"geometry"

# add the area that is possibly mainly agricultural land to the swissTLM3D Bodenbedeckung
bodenbedeckung<-rbind(boden, landwirtschaft)

# cbind the descriptions of the SWISS TLM3D catalogue
objektart<-c(5,6,7,10,11,12,14, 1000)
objektbesch_DE<-c("Fliessgewaesser", "Gebueschwald", "Lockergestein",
                  "stehende Gewaesser", "Feuchtgebiet", "Wald",
                  "Gehoelzflaechen", "Landwirtschaft")
object_desc<-c("bodies of running water", "bush forest", "loose rock",
               "bodies of stagnant water", "wetland", "forest", 
               "woodland","agriculture")
object_description<-as.data.frame(cbind(objektart, objektbesch_DE,
                                        object_desc))
# join descriptions and geometries of "bodenbedeckung swissTLM3D"
bb_desc<-inner_join(bodenbedeckung, object_description, by="objektart")

rm(boden, bodenbedeckung)
```
The descriptions of the ground cover (swissTLM3D Bodenbedeckung) were taken from the __Objektkatalog__ ( __swisstopo, 2022__).
```{r }

f_encounters<-st_join(f_encounters, bb_desc)
m_encounters<-st_join(m_encounters, bb_desc)
```


```{r }
# Selection of the rows within 1h,2h, 3h, 4h, 5h, and 6h after the encounter
f_1h<- f_encounters %>%
  filter(rowid.x== rowid.y | rowid.x== rowid.y+1 | 
           rowid.x== rowid.y+2 | rowid.x== rowid.y+3) %>%
  group_by(meet_id) %>%
  mutate(encounter= "1h")
f_2h<- f_encounters %>%
  filter(rowid.x %in% c(rowid.y+4, rowid.y+5, rowid.y+6, rowid.y+7)) %>%
  group_by(meet_id)%>%
  mutate(encounter= "2h")
f_3h<- f_encounters %>%
  filter(rowid.x %in% c(rowid.y+8, rowid.y+9, rowid.y+10, rowid.y+11)) %>%
  group_by(meet_id)%>%
  mutate(encounter= "3h")
f_4h<- f_encounters %>%
  filter(rowid.x %in% c(rowid.y+12, rowid.y+13, rowid.y+14, rowid.y+15)) %>%
  group_by(meet_id)%>%
  mutate(encounter= "4h")
f_5h<- f_encounters %>%
  filter(rowid.x %in% c(rowid.y+16, rowid.y+17, rowid.y+18, rowid.y+19)) %>%
  group_by(meet_id)%>%
  mutate(encounter= "5h")
f_6h<- f_encounters %>%
  filter(rowid.x %in% c(rowid.y+20, rowid.y+21, rowid.y+22, rowid.y+23)) %>%
  group_by(meet_id)%>%
  mutate(encounter= "6h")

m_1h<- m_encounters %>%
  filter(rowid.x== rowid.y | rowid.x== rowid.y+1 | 
           rowid.x== rowid.y+2 | rowid.x== rowid.y+3) %>%
  group_by(meet_id)%>%
  mutate(encounter= "1h")
m_2h<- m_encounters %>%
  filter(rowid.x %in% c(rowid.y+4, rowid.y+5, rowid.y+6, rowid.y+7)) %>%
  group_by(meet_id)%>%
  mutate(encounter= "2h")
m_3h<- m_encounters %>%
  filter(rowid.x %in% c(rowid.y+8, rowid.y+9, rowid.y+10, rowid.y+11)) %>%
  group_by(meet_id)%>%
  mutate(encounter= "3h")
m_4h<- m_encounters %>%
  filter(rowid.x %in% c(rowid.y+12, rowid.y+13, rowid.y+14, rowid.y+15)) %>%
  group_by(meet_id)%>%
  mutate(encounter= "4h")
m_5h<- m_encounters %>%
  filter(rowid.x %in% c(rowid.y+16, rowid.y+17, rowid.y+18, rowid.y+19)) %>%
  group_by(meet_id)%>%
  mutate(encounter= "5h")
m_6h<- m_encounters %>%
  filter(rowid.x %in% c(rowid.y+20, rowid.y+21, rowid.y+22, rowid.y+23)) %>%
  group_by(meet_id)%>%
  mutate(encounter= "6h")

# selection of the rows 1h before the encounter
f_1h_sub<- f_encounters %>%
  filter(rowid.x %in% c(rowid.y-1, rowid.y-2, rowid.y-3, rowid.y-4)) %>%
  group_by(meet_id)%>%
  mutate(encounter= "sub_1h")
m_1h_sub<- m_encounters %>%
  filter(rowid.x== rowid.y-1 | rowid.x== rowid.y-2 | 
           rowid.x== rowid.y-3 | rowid.x== rowid.y-4) %>%
  group_by(meet_id)%>%
  mutate(encounter= "1hbefore")


# selection of the 6h after the encounter (because of different sampling intervals during the day it's not exactly 6h, but close enough (hopefully))
f_6h<- rbind( f_1h, f_2h, f_3h, f_4h, f_5h, f_6h) %>%
  group_by(meet_id)
m_6h<- rbind( m_1h, m_2h, m_3h, m_4h, m_5h, m_6h) %>%
  group_by(meet_id)

rm(f_2h, f_3h, f_4h, f_5h, m_2h, m_3h, m_4h, m_5h)
```




## Results


### Comparison speeds of female and male wild boars within 1h of the encounter

H0: The difference in the speeds of female and male wild boars have no systematic reason but occurred at random.
H1: The difference in the speeds of female and male wild boars have a systematic reason.
```{r }
#comparisons of male/ female: speed 1h after encounter, distance 1h after encounter, distance by volume, distance by modus, (if possible) similarities of trajectories coming from the same deterrence locations (I don't have the forest/field edges, but possibly they run straight to the next cover which means their trajectories would be really similar) 

# testing for normality
shapiro.test(f_1h$speed)
shapiro.test(m_1h$speed)
# since f_speeds data not normal, independent --> wilcox
wilcox.test(f_1h$speed, m_1h$speed)
# H0 TRUE: speeds f/m not systematically different

f_1_comparison<-f_1h %>%
  st_drop_geometry() %>%
  ungroup() %>%
  mutate(sex="female")%>%
  select(speed, sex)
m_1_comparison<-m_1h %>%
  st_drop_geometry() %>% 
  ungroup() %>%
  mutate(sex="male") %>%
  select(speed, sex)
comparison<- rbind(f_1_comparison, m_1_comparison)
comparison<-comparison %>%
  group_by(sex)

p_fm_speed<-ggplot(data=comparison, aes(sex, speed, fill=sex))+
  geom_boxplot(width=.6, color="#525252")+
  labs(title=" \n Comparison of female and male speed one hour \n after the encounter with a deterrence \n")+
  ylab("speed [m/s]")+
  scale_fill_manual(values=c(col_7[2], col_7[5]))+
  theme_minimal()+
  theme(legend.position="none")  
p_fm_speed
rm(f_1h_comparison, m_1h_comparison, comparison)
```


```{r }
#Does volume, interval or modus have an influence on speed 1h after encounter

#(volume is the sound intensity, as a percentage of the max value (120dB in 1 m distance))
# since we know the data does not have normal distribution -->

#females
kruskal.test(speed~modus, data=f_1h)
kruskal.test(speed~lautstaerke, data=f_1h) 


#males
kruskal.test(speed~modus, data=m_1h) 
kruskal.test(speed~lautstaerke, data=m_1h) 

# boxplots speed-modus
f_speed_modus<- f_1h %>%
  group_by(modus) %>%
  ggplot() + 
  geom_boxplot(aes(x=modus, y=speed, group=modus, fill=modus), color="#525252") +
  xlab("Mode\n")+
  ylab("speed [m/s]\n")+
  scale_fill_manual(values=c(col_7[1], col_7[2], col_7[4]))+
  theme_minimal()+
  labs(fill="Mode")+
  ylim(0,1)

m_speed_modus<- m_1h %>%
  group_by(modus)%>%
  ggplot()+
  geom_boxplot(aes(x=modus, y=speed, group=modus, fill=modus), color="#525252") +
  xlab("Mode\n")+
  ylab("speed [m/s]\n")+
  scale_fill_manual(values=c(col_7[1], col_7[2]))+
  theme_minimal()+
  theme(legend.position="none") +
  ylim(0,1)

# boxplots speed-lautstaerke
f_speed_vol<- f_1h %>%
  group_by(lautstaerke) %>%
  ggplot() + 
  geom_boxplot(aes(x=as.factor(lautstaerke*1.2), y=speed, fill=as.factor(lautstaerke*1.2)),
               color="#525252") +
  xlab("Volume [db]\n")+
  ylab("speed [m/s]\n")+
  scale_fill_manual(values=c(col_7[5], col_7[4], col_7[2], col_7[1]))+
  theme_minimal()+
  labs(fill="Volume")+
  ylim(0,1)

m_speed_vol<- m_1h %>%
  group_by(lautstaerke)%>%
  ggplot()+
  geom_boxplot(aes(x=as.factor(lautstaerke*1.2), y=speed,  fill=as.factor(lautstaerke*1.2)),
               color="#525252")+
  xlab("Volume [db]\n")+
  ylab("speed [m/s]\n")+
  scale_fill_manual(values=c( col_7[5], col_7[4]))+
  theme_minimal()+
  theme(legend.position="none")+
  ylim(0,1)

p_speed_modusvolume<-(f_speed_modus+m_speed_modus)/(f_speed_vol+m_speed_vol) +
  plot_annotation(title="Speed dependant on deterrence mode and volume", subtitle="Females                                                                                         Males")
p_speed_modusvolume
rm(f_speed_modus, m_speed_modus, f_speed_vol, m_speed_vol)
```

Comparison of distance 1h after encounter
```{r }
f_1h_dist<-f_1h %>%
  st_drop_geometry() %>%
  group_by(meet_id, lautstaerke, modus, intervall)%>%
  summarise(dist=sum(steplength, na.rm=T))

m_1h_dist<-m_1h %>%
  st_drop_geometry() %>%
  group_by(meet_id, lautstaerke, modus)%>%
  summarise(dist=sum(steplength, na.rm=T))

# testing for normality
shapiro.test(f_1h_dist$dist) #not normal
shapiro.test(m_1h_dist$dist) # normal (how, but whatever)
# since f_speeds data not normal, independent --> wilcox
wilcox.test(f_1h_dist$dist, m_1h_dist$dist)
# H0 TRUE: distance f/m not systematically different

f_1_dist<-f_1h_dist %>%
  ungroup() %>%
  mutate(sex="female")%>%
  select(dist, sex)
m_1_dist<-m_1h_dist %>%
  ungroup() %>%
  mutate(sex="male") %>%
  select(dist, sex)
comparison_dist<- rbind(f_1_dist, m_1_dist)
comparison_dist<-comparison_dist %>%
  group_by(sex)

p_fm_dist<-ggplot(data=comparison_dist, aes(sex, dist, fill=sex))+
  geom_boxplot(width=.6, color="#525252")+
  labs(title="Comparison of female and male flight distance within one hour \n after the encounter with a deterrence")+
  ylab("distance [m]")+
  scale_fill_manual(values=c(col_7[2], col_7[5]))+
  theme_minimal()+ 
  theme(legend.position="none") 
p_fm_dist
rm(f_1_dist, m_1_dist, comparison_dist)
```
Does volume or modus have an influence on distance 1h after encounter
```{r }
# since we know the data does not have normal distribution -->
#females
kruskal.test(dist~modus, data=f_1h_dist)
kruskal.test(dist~lautstaerke, data=f_1h_dist) 


#males
kruskal.test(dist~modus, data=m_1h_dist) 
kruskal.test(dist~lautstaerke, data=m_1h_dist) 
```

```{r }
# boxplots distance-modus
f_dist_modus<- f_1h_dist %>%
  group_by(modus) %>%
  ggplot() + 
  geom_boxplot(aes(x=modus, y=dist, group=modus, fill=modus), color="#525252") +
  xlab("Mode \n")+
  ylab("Distance [m] \n")+
  scale_fill_manual(values=c(col_7[1], col_7[2], col_7[4]))+
  theme_minimal()+
  labs(fill="Mode")+
  ylim(0,2500)

m_dist_modus<- m_1h_dist %>%
  group_by(modus)%>%
  ggplot()+
  geom_boxplot(aes(x=modus, y=dist, group=modus, fill=modus), color="#525252", width=.5) +
  xlab("Mode \n")+
  ylab("Distance [m] \n")+
  scale_fill_manual(values=c(col_7[1], col_7[2]))+
  theme_minimal()+
  theme(legend.position="none")+
  ylim(0,2500)

# boxplots distance-lautstaerke
f_dist_vol<- f_1h_dist %>%
  group_by(lautstaerke) %>%
  ggplot() + 
  geom_boxplot(aes(x=as.factor(lautstaerke*1.2), y=dist, fill=as.factor(lautstaerke*1.2)),
               color="#525252", width=.5) +
  xlab("Volume [db] \n ")+
  ylab("Distance [m] \n")+
  scale_fill_manual(values=c(col_7[5], col_7[4], col_7[2], col_7[1]))+
  theme_minimal()+
  labs(fill="Volume")+
  ylim(0,2500)

m_dist_vol<- m_1h_dist %>%
  group_by(lautstaerke)%>%
  ggplot()+
  geom_boxplot(aes(x=as.factor(lautstaerke*1.2), y=dist,  fill=as.factor(lautstaerke*1.2)),
               color="#525252", width=.5)+
  xlab("Volume [db] \n")+
  ylab("Distance [m] \n")+
  scale_fill_manual(values=c( col_7[5], col_7[4]))+
  theme_minimal()+
  theme(legend.position="none")+
  ylim(0,2500)


p_dist_modusvolume<-(f_dist_modus+m_dist_modus)/(f_dist_vol+m_dist_vol) +
  plot_annotation(title="Distance dependant on deterrence mode and volume", subtitle="Females                                                                                         Males")
p_dist_modusvolume
rm(f_dist_modus, m_dist_modus, f_dist_vol, m_dist_vol)
```
Comparing distances of each hour (1-6) after the encounter
```{r }
f_dist<-f_6h %>%
  st_drop_geometry() %>%
  group_by(encounter, meet_id)%>%
  summarise(dist=sum(steplength, na.rm=T))
kruskal.test(dist~encounter, data=f_dist) 

m_dist<-m_6h %>%
  st_drop_geometry() %>%
  group_by(encounter, meet_id)%>%
  summarise(dist=sum(steplength, na.rm=T))
kruskal.test(dist~encounter, data=m_dist) 

p_f_dist<- f_dist %>%
  group_by(encounter) %>%
  ggplot(color="#525252") + 
  geom_boxplot(aes(x=encounter, y=dist, group=encounter, fill=encounter))+
  scale_fill_manual(values=col_7)+
  xlab("hour(s) after the encounter")+
  ylab("Distance [m] \n")+
  theme_minimal()+
  theme(legend.position="none")+
  ylim(0,1800)+
  labs(title="\n Covered distances of female wild boars in the six hours after encounter \n")

p_m_dist<- m_dist %>%
  group_by(encounter) %>%
  ggplot(color="#525252") + 
  geom_boxplot(aes(x=encounter, y=dist, group=encounter, fill=encounter))+
  scale_fill_manual(values=col_7)+
  xlab("hour(s) after the encounter")+
  ylab("Distance [m] \n")+
  theme_minimal()+
  theme(legend.position="none")+
  ylim(0,1800)+
  labs(title="\n Covered distances of male wild boars in the six hours after encounter \n")

p_f_dist/p_m_dist
rm(f_dist, m_dist)

```

```{r }
f_1v2<-f_6h %>%
  filter(encounter %in% c("1h", "2h")) %>%
  st_drop_geometry() %>%
  group_by(encounter, meet_id) %>%
  summarise(dist=sum(steplength, na.rm=T))
f_1v2<- kruskal.test(dist~encounter, data=f_1v2) # p-value = 0.001165 - the difference in distance between the first and second hour after the encounter is significant
f_1v3<-f_6h %>%
  filter(encounter %in% c("1h", "3h")) %>%
  st_drop_geometry() %>%
  group_by(encounter, meet_id) %>%
  summarise(dist=sum(steplength, na.rm=T))
f_1v3<-kruskal.test(dist~encounter, data=f_1v3) # p-value = 0.0005569 - the difference in distance between the first and third hour after the encounter is significant

f_1v4<-f_6h %>%
  filter(encounter %in% c("1h", "4h")) %>%
  st_drop_geometry() %>%
  group_by(encounter, meet_id) %>%
  summarise(dist=sum(steplength, na.rm=T))
f_1v4<-kruskal.test(dist~encounter, data=f_1v4) # p-value = 5.102e-05 - the difference in distance between the first and fourth hour after the encounter is significant

f_1v5<-f_6h %>%
  filter(encounter %in% c("1h", "5h")) %>%
  st_drop_geometry() %>%
  group_by(encounter, meet_id) %>%
  summarise(dist=sum(steplength, na.rm=T))
f_1v5<-kruskal.test(dist~encounter, data=f_1v5) # p-value = 9.322e-08 - the difference in distance between the first and fifth hour after the encounter is significant

f_1v6<-f_6h %>%
  filter(encounter %in% c("1h", "6h")) %>%
  st_drop_geometry() %>%
  group_by(encounter, meet_id) %>%
  summarise(dist=sum(steplength, na.rm=T))
f_1v6<-kruskal.test(dist~encounter, data=f_1v6) # p-value = 5.403e-10 - the difference in distance between the first and sixth hour after the encounter is significant

m_1v2<-m_6h %>%
  filter(encounter %in% c("1h", "2h")) %>%
  st_drop_geometry() %>%
  group_by(encounter, meet_id) %>%
  summarise(dist=sum(steplength, na.rm=T))
m_1v2<-kruskal.test(dist~encounter, data=m_1v2) # p-value = 0.3732 

m_1v3<-m_6h %>%
  filter(encounter %in% c("1h", "3h")) %>%
  st_drop_geometry() %>%
  group_by(encounter, meet_id) %>%
  summarise(dist=sum(steplength, na.rm=T))
m_1v3<-kruskal.test(dist~encounter, data=m_1v3) # p-value = 0.03685 - the difference in distance between the first and third hour after the encounter is significant

m_1v4<-m_6h %>%
  filter(encounter %in% c("1h", "4h")) %>%
  st_drop_geometry() %>%
  group_by(encounter, meet_id) %>%
  summarise(dist=sum(steplength, na.rm=T))
m_1v4<-kruskal.test(dist~encounter, data=m_1v4) # p-value = 0.007494 - the difference in distance between the first and fourth hour after the encounter is significant

m_1v5<-m_6h %>%
  filter(encounter %in% c("1h", "5h")) %>%
  st_drop_geometry() %>%
  group_by(encounter, meet_id) %>%
  summarise(dist=sum(steplength, na.rm=T))
m_1v5<-kruskal.test(dist~encounter, data=m_1v5) # p-value = 0.06378 - the difference in distance between the first and fifth hour after the encounter is significant

m_1v6<-m_6h %>%
  filter(encounter %in% c("1h", "6h")) %>%
  st_drop_geometry() %>%
  group_by(encounter, meet_id) %>%
  summarise(dist=sum(steplength, na.rm=T))
m_1v6<-kruskal.test(dist~encounter, data=m_1v6) # p-value = 0.008071 - the difference in distance between the first and sixth hour after the encounter is significant

kruskal_hourscomparison<-c(f_1v2[3],f_1v3[3],f_1v4[3],f_1v5[3],f_1v6[3],
                           m_1v2[3], m_1v3[3], m_1v4[3],m_1v5[3],m_1v6[3])
rm(f_1v2,f_1v3,f_1v4, f_1v5, f_1v6, m_1v2, m_1v3,m_1v4, m_1v5, m_1v6)
```

Now, which wild boars came back to a field with a deterrence several times?
```{r }
f_returenees <- f_unique %>%
  st_drop_geometry() %>%
  group_by(TierName) %>%
  count()
m_returenees <- m_unique %>%
  st_drop_geometry() %>%
  group_by(TierName) %>%
  count()


```

```{r }
# fix the colors of this SHIT !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
ggplot()+
  geom_sf(data=bb_desc, aes(fill=object_desc, color=object_desc), alpha=.5) +
  geom_sf(data=f_1h, color=col_7[1], shape=1)+
  geom_sf(data=m_1h, color=col_7[7], shape=2)+
  coord_sf(datum=2056)


f_groundcover <- f_6h %>%
  st_drop_geometry() %>%
  group_by(encounter, object_desc) %>%
  count()
m_groundcover <- m_6h %>%
  st_drop_geometry() %>%
  group_by(encounter, object_desc) %>%
  count() 

# !!!!!!!!!!!!!!!!!!!!!!COLORS
ggplot()+
  geom_bar(data=f_groundcover, aes(x=encounter, y=n, fill=object_desc), stat="identity", position="fill")+
  scale_fill_manual(values=col_7[6:1])
  

ggplot()+
  geom_bar(data=m_groundcover, aes(x=encounter, y=n, fill=object_desc), stat="identity", position="fill")
```

```{r }
swissimage<-terra::rast("swissimage_wild_boar.tif")

swissimg<-tm_shape(swissimage)+
  tm_rgb()
  
swissimg + tm_shape(m_1h)+
  tm_dots(col=col_7[3], shape=1, size=.2)+
  tm_shape(f_1h)+
  tm_dots(col=col_7[2], shape=1, size=.2)
  
```

## Discussion

  
